Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-19 manuscript/ERL_global_C_review.Rmd
update CUE

TrB_age_trends_caption = "Figure 9 | Age trends in C cycling in tropical broadleaf forests. Selection of variables for plotting seeks to maximize sample size and broad geographic representation while representing all elements of C cycle. Asterisks indicate variables whose age trends were calculated based on other variables (*young and mature forests; **young forests only; ***mature forests only), as follows: $R_{auto-ag}=R_{auto}-R{root}$, where $R_{auto}=NPP(1/CUE-1)$, where $CUE$ is TEMPORARILY 0.5; $ANPP_{woody}=max(0,ANPP-ANPP_{foliage})$; $B_{ag-wood}=max(0,B_{ag}-B_{foliage})$; $B_{root-coarse}=max(0,B_{root}-B_{root-fine})$; $DW_{standing}=max(0, DW_{tot}-DW_{down})$."
age_trends_caption_generic= "Selection of variables for plotting seeks to maximize sample size and broad geographic representation while representing all elements of C cycle. Asterisks indicate variables whose age trends were calculated based on other variables (*young and mature forests; **young forests only; ***mature forests only), as follows: $R_{auto-ag}=R_{eco}-R{soil}$; ANPP_{woody}=min(ANPP_{stem},ANPP_{woody}); $B_{ag-wood}=max(0,B_{ag}-B_{foliage})$; $B_{root-coarse}=max(0,B_{root}-B_{root-fine})$; $DW_{standing}=max(0, DW_{tot}-DW_{down})$."
TeB_age_trends_caption = paste("Figure 10 | Age trends in C cycling in temperate broadleaf forests.", age_trends_caption_generic) 
TeN_age_trends_caption = paste("Figure 11 | Age trends in C cycling in temperate conifer forests.", age_trends_caption_generic) 
BoN_age_trends_caption = paste("Figure 12 | Age trends in C cycling in boreal conifer forests.", age_trends_caption_generic)

@@

@@

C fluxes commonly increased significantly with stand age (Tables 1, S2, Figs. `r flux_age_trends`, `r TrB_age_trends`-`r BoN_age_trends`, `r all_age_trends`).
*ForC* contained 16 C flux variables with sufficient data for analyses of age trends in young forests (see Methods).
Of these, ten increased significantly with $log10[age]$: $NEP$, $GPP$, $ANPP$, $ANPP_{woody}$, $ANPP_{foliage}$, $ANPP_{litterfal}$, $BNPP$, $BNPP_{fine}$, $R_{eco}$, and $R_{root}$.
The remaining six--$NPP$, $ANPP_{stem}$, $ANPP_{branch}$, $BNPP_{coarse}$, **$R_{soil-het}$, and $R_{soil-het}$**-–displayed no significant relationship to stand age.

@@

  knitr::include_graphics("tables_figures/stacked_age_trends/Boreal conifer_age_trends.png")
```
*(paragraph on young vs mature)*

@@

>>>>

TrB_age_trends_caption = "Figure 9 | Age trends in C cycling in tropical broadleaf forests. Selection of variables for plotting seeks to maximize sample size and broad geographic representation while representing all elements of C cycle. Asterisks indicate variables whose age trends were calculated based on other variables (* young and mature forests; ** young forests only; *** mature forests only), as follows: $R_{auto-ag}=R_{auto}-R{root}$, where $R_{auto}=NPP(1/CUE-1)$, where $CUE$=0.46 (Collati et al. 2020); $ANPP_{woody}=max(0,ANPP-ANPP_{foliage})$; $B_{ag-wood}=max(0,B_{ag}-B_{foliage})$; $B_{root-coarse}=max(0,B_{root}-B_{root-fine})$; $DW_{standing}=max(0, DW_{tot}-DW_{down})$."
age_trends_caption_generic= "Selection of variables for plotting seeks to maximize sample size and broad geographic representation while representing all elements of C cycle. Asterisks indicate variables whose age trends were calculated based on other variables (* young and mature forests; ** young forests only; *** mature forests only), as follows: $R_{auto-ag}=R_{eco}-R{soil}$; $ANPP_{woody}=min(ANPP_{stem},ANPP_{woody})$; $B_{ag-wood}=max(0,B_{ag}-B_{foliage})$; $B_{root-coarse}=max(0,B_{root}-B_{root-fine})$; $DW_{standing}=max(0, DW_{tot}-DW_{down})$."
TeB_age_trends_caption = paste("Figure 10 | Age trends in C cycling in temperate broadleaf forests.", age_trends_caption_generic) 
TeN_age_trends_caption = paste("Figure 11 | Age trends in C cycling in temperate conifer forests.", age_trends_caption_generic) 
BoN_age_trends_caption = paste("Figure 12 | Age trends in C cycling in boreal conifer forests.", age_trends_caption_generic)

@@

---
nocite: | 
@collalti_forest_2020
---

@@

C fluxes commonly increased significantly with stand age (Tables 1, S2, Figs. `r flux_age_trends`, `r TrB_age_trends`-`r BoN_age_trends`, `r all_age_trends`).
*ForC* contained 16 C flux variables with sufficient data for analyses of age trends in young forests (see Methods).
Of these, ten increased significantly with $log10[age]$: $NEP$, $GPP$, $ANPP$, $ANPP_{woody}$, $ANPP_{foliage}$, $ANPP_{litterfal}$, $BNPP$, $BNPP_{fine}$, $R_{eco}$, and $R_{root}$.
The remaining six--$NPP$, $ANPP_{stem}$, $ANPP_{branch}$, $BNPP_{coarse}$, $R_{soil}$, and $R_{het-soil}$-–displayed no significant relationship to stand age.

@@

  knitr::include_graphics("tables_figures/stacked_age_trends/Boreal conifer_age_trends.png")
```

@@

There were also some substantial discrepancies between 
*(paragraph on young vs mature)*
